---
title: "Pair programming demo solutions"
author: "Karim Rivera-Lares"
date: "2025-08-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **What is pair programming?**

Pair programming refers to a common practice in software development where two programmers work on the same coding task at the same time.

Both programmers work on one computer (although they can work remotely), with one acting as *the driver*, controlling the keyboard and mouse, and the other one acting as *the navigator*, reviewing the code as it's written and offering suggestions.

Pair programmers often find this technique allows them to be more productive and write higher-quality code because they are discussing, reviewing, and testing the code as it gets written.

The roles should be swapped regularly.

## **Pair Programming Demo: Average Weight of Women**

**Step 1:** Decide who will be the driver and who will be the navigator.

**Step 2**: Start the task :)

**Task**: Calculate average weight, plot distribution, and mark the mean.

**Dataset:** `women` (built-in in R)

1.  Let's start by checking the dataset.

```{r}

```

2.  Calculate the average weight

```{r}

```

3.  Make a histogram to see the distribution of weights.

```{r}

```

4.  Make it prettier.

```{r}

```

5.  Add a vertical line showing the average weight.

```{r}

```

6.  Calculate median weight and compare to the mean

```{r}

```

7.  Make a boxplot to visualise the distribution

```{r}

```
