---
title: "Week 1 exercise set 2"
author: "Data Science Course Team"
date: "2025-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Please complete the exercises below in your pair. Remember to switch who is 
driving after each task.

# Exercise 1

Assume the following definitions for a survey:

-   A person with an age from 1 to 17 years is classified as a minor;

-   a person with an age from 18 to 64 years is classified as an adult;

-   a person with an age from 65 to 99 years is classified as a senior.

Generate a vector with 100 random samples that specifies the age of 100 people (in years), but contains exactly 20 minors, 50 adults, and 30 seniors.

```{r}

```

# Exercise 2

What is the average (mean), minimum, and maximum age in this sample?

```{r}

```

# Exercise 3

How many people are younger than 25 years?

```{r}

```

# Exercise 4

What is the average (mean) age of people older than 50 years?

```{r}

```

# Exercise 5

How many people have a round age (i.e., an age that is divisible by 10)? What is their mean age?

HINT: For this task, you'll need to use the modulo operator, which gives you the remainder of integer division. Look it up if you're not familiar with it.

```{r}

```
