---
title: "Hospital Length of Stays"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(NHSRdatasets)
library(knitr)
library(gt)
```

# Load the data

*The data we'll be working with are part of the NHSRdatasets package*

```{r}
data("LOS_model")
?LOS_model
```

# Inspect

*Use your favourite functions to find out more about this dataset*

```{r}


```

This table has `r nrow(LOS_model)` rows and `r ncol(LOS_model)` columns.

# Tidying up Death

*Make Death a factor*

```{r}

```

*Recode Death levels*

```{r}

```

# Summary table

*Create a summary table where each combination of Organisation and Death gets a count (n).*

```{r}

```

# Wide table

*Make a wide table with Dead and Survived as rows with a column for each Trust*

```{r}

```

# Trust table

*Another pivot with Survived and Died as columns, Trusts as rows. Also calculate the % survived for each Trust*

```{r}

```

# Pretty table

*Make the wide table pretty with gt()*

```{r}

```

# The end

*Let's knit to html to see your nice report (use the Knit button in RStudio, at the top of your editor window)*
