---
title: "Week 02 - conditions and logical indexing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 01: conditions 1

Examine the code and decide on whether a condition will be `TRUE` or `FALSE`. Write down the answer and then run the chunk to check the answer.

**Answer 1:**

```{r exercise 01-1}
x <- 4
(x > 3)
```

**Answer 2:**

```{r exercise 01-2}
x <- 4
y <- 5
(x != y)
```

## Exercise 02: conditions 2

Examine the code and decide on whether a condition will be `TRUE` or `FALSE`. Write down the answer and then run the chunk to check the answer.

**Answer 1:**

```{r exercise 02-1}
x <- 4
!(x < 3)
```

**Answer 2:**

```{r exercise 02-2}
x <- 4
y <- 5
!(x != y)
```

## Exercise 03: conditions 3

Examine the code and decide on whether a condition will be `TRUE` or `FALSE`. Write down the answer and then run the chunk to check the answer.

**Answer 1:**

```{r exercise 03-1}
x <- 4
(x < 3) | (x >=4)
```

**Answer 2:**

```{r exercise 03-2}
x <- 4
y <- 6
(x == y) | ((x < 5) & (y > 5))
```

**Answer 3:**

```{r exercise 03-3}
x <- 3
y <- 3
(x != y) & ((x <= 3) & (y >= 3))
```

**Answer 4:**

```{r exercise 03-4}
x <- 3
y <- 3
(x != y) | ((x <= 3) & (y >= 3))
```

## Exercise 04: conditions

Examine the code and decide on whether a condition will be `TRUE` or `FALSE`. Write down the answer and run the chunk to check the answer.

**Answer 1:**

```{r exercise 04-1}
x <- seq(-4, 4, 2)
(x == 0)
```

**Answer 2:**

```{r exercise 04-2}
x <- seq(-4, 4, 2)
y <- 1:5
(x + y <= 0)
```

**Answer 3:**

```{r exercise 04-3}
x <- seq(-4, 12, 4)
y <- 1:5
(x > y)
```

**Answer 4:**

```{r exercise 04-4}
x <- seq(-4, 12, 4)
y <- 1:5
(x > y) & ((x < 10) | (y < 3))
```

## Exercise 05: logical indexing

Use logical indexing to values of `x` that are above 3.

```{r exercise 05-1}
x <- -3:7
# Your code goes here
```

Use logical indexing to extract values of `x` when it is higher than value in `y`

```{r exercise 05-2}
x <- -3:7
y <- seq(5, -2, length.out = 11)
# Your code goes here
```

Use logical indexing to extract values of `x` that are greater than the mean value of x (avoid using intermediate variables).

```{r exercise 05-3}
x <- -3:7
# Your code goes here
```
