---
title: "Week 02 - dplyr exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 01: select
Use [diamonds](https://ggplot2.tidyverse.org/reference/diamonds.html) example table from `ggplot2` package.

Select only `price`, `cut`, and `color` columns. Use piping and `select`.
```{r exercise 01-1}
```

Select only `price`, `cut`, and `color` columns. Use base R (no piping or select).
```{r exercise 01-2}
```

Select all columns except for `x`, `y`, and `z`. Use negative selection and piping.
```{r exercise 01-3}
```

Check out the help page for the `select()` function. Use `:` notation to select columns from `carat` till `clarity`.
```{r exercise 01-4}
```

And now select these same columns by capitalising on the fact that all their names (and none of the others) start with the letter "c".

```{r exercise 01-5}

```

BONUS: How would you select these 4 columns in base R, without simply listing their names?

```{r exercise 01-6}

```


## Exercise 02: filter
Use [msleep](https://ggplot2.tidyverse.org/reference/msleep.html) example table from `ggplot2` package. 

Filter the table to keep only `"domesticated"` animals (variable name is `conservation`).
```{r exercise 02-1}
```

Filter the table to keep only the omnivores (`vore`) that sleep more than 10 hours in total.
```{r exercise 02-2}
```

Filter the table to exclude animals with body weight above `50`.
```{r exercise 02-3}
```

Filter the table to exclude animals with body weight below [median](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/median.html) body weight. Hint, you do not need a temporary variable. 
```{r exercise 02-4}
```


## Exercise 03: arrange
Use [presidential](https://ggplot2.tidyverse.org/reference/presidential.html) example table from _ggplot2_ package.

Arrange the table by party.
```{r exercise 03-1}

```

Arrange the table by start date in the descending order.
```{r exercise 03-2}

```

Arrange the table by party (descending order) and president's name (ascending order).
```{r exercise 03-3}

```


## Exercise 4: mutate

Use [msleep](https://ggplot2.tidyverse.org/reference/msleep.html) example table from `ggplot2` package.

Compute new variable / column with sleep to body weight ratio.
```{r exercise 04-1}

```

Compute new variable / column `is_big` of logical value that are `TRUE` if body weight is above `50`.
```{r exercise 04-2}

```

Compute three new variables / columns. First, compute the _mean_ and _standard deviation_ of total sleep variable. You will get the same value in all the rows, make sure that your columns are _not_ called `mean` and `sd`. Then compute a z-score of the total sleep: $Z(x) = (x - mean(x)) / sd(x)$. Put all computations into a single mutate code.
```{r exercise 04-3}
```

Compute z-score for body weight variable, do not store mean and standard deviation in extra columns but use them directly.
```{r exercise 04-4}
```

