---
title: "Week 02 - tidyr"
output: html_document
---

## Introduction

```{r load-data}
install.packages("ds4psy")
#the line below loads the posPsy_wide dataset without needing to load the entire ds4psy package
posPsy_wide <- ds4psy::posPsy_wide 
```

This dataset contains the results of a psychological intervention study. Each participant was seen 6 times, and each time they responded to two questionnaires: the Authentic Happiness Inventory (AHI) and the Center for Epidemiological Studies Depression scale (CES-D).

Column names starting with `ahi` and `cesd` contain people's scores on each item, on each occasion. For example, `cesd04.0` refers to the score on the 4th item of the CES-D questionnaire, at occasion 0 (i.e. at baseline).

For additional information about this dataset (including a codebook), see: <https://bookdown.org/hneth/ds4psy/B.1-datasets-pos.html>

## Exercise 1
How many questions (items) were in the the Authentic Happiness Inventory (AHI), and how many in the Centre for Epidemiological Studies Depression scale (CES-D)? Try to find the answer without looking at the codebook or scrolling through the dataset, but you can check the variable names.

```{r item-numbers}

```


## Exercise 2
Create a subset of the data with only the following columns: id, intervention, and the totals of each participant's scores on the CES-D at each occasion. Save this into a new object called `cesd_totals`.

HINT: You could call each of the columns separately. But, to save typing, you can also use the `starts_with` helper to select multiple columns. Check out the documentation for `select()` to learn more about this approach. 

```{r cesd-totals}

```


## Exercise 3
We want to check whether the way that CES-D score changed over time was dependent on the specific intervention that the participants got. There were 4 different intervention groups, and they are indicated in the `intervention` column.

Let's start by creating a summary table - each column should show the average CES-D score at a given occasion, and each row should be a different intervention group. 

Draw the table on paper first, and then discuss how you would go creating it in R. Finally, create the table, using the newly created `cesd_totals` dataset.

```{r cesd-means}

```


## Exercise 4
Now, try to create a graph based on your table. We would like to see a line graph showing the change in CES-D scores over time, with each intervention group drawn in a different colour.

NOTE: This exercise is tricky and you'll likely get stuck. If you do, move on to Exercise 5.

```{r graph-first-attemps}

```


## Exercise 5
To make the required graph, you'll need the data to be in a different format - referred to as the "long format". We want to see 3 only columns: `occasion`, `intervention` and `mean_cesd`. You'll need to pivot your data into this format. If you're struggling to code it, draw the tables on paper first - what are the changes that need to happen? Call your table `cesd_means_long`.

```{r pivot-to-long}

```


## Exercise 6
Now that your data are in a suitable format, create the graph described in Exercise 4.

NOTE: If your interventions are all plotted in different shades of the same colour, something went wrong. Investigate and change your code so that each intervention is plotted as a different colour. 

```{r graph-second-attempt}

```


## Exercise 7
Just to practice pivoting again, try turning `cesd_means_long` back into the wide format. 

Can you get the column names to be more informative than just numbers? Look at the documentation of `pivot_wider()` to help you.

```{r pivot-to-wide}

```





